Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-24 paper/main.tex

Borda and uBorda are equivalent when $w(\sigma)$ is constant for every $\sigma$. However, in other case uBorda ranking will be closer to the rankings in $S$ with smaller value of $w(\sigma)$. Roughly speaking, it is equivalent to replicating in the sample the $\sigma$ with low values of $w(\sigma$).
%Intuitively, the uBorda ranking a given sample of permutations $S$\MANUEL{X What is $S$?} is equivalent to the Borda ranking of $S'$, being $S'$ an extension of $S$ where each each $\sigma\in S$ has been replicated proportionally to its weight $w(\sigma)$.\MANUEL{X so $w$ is a weight function from $w\colon S_n \to \mathbb{R}$?} %
Clearly, the choice of  $w(\sigma)$ depends on the relevant property of a ranking in a particular domain. For example, uBorda has been shown to have nice theoretical properties for the online estimation of the parameters of a sample with concept drift~\cite{}.\MANUEL{X where? Do we miss a citation here?\ekhine{}{to be processed, arxiv}}

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and
the GA that optimizes the surrogate models uses a population size of 20,
crossover rate of 0.5, mutation rate of 1, tournament selection of size 2 and
probability of 0.9, interchange mutation (i.e., exchanging two randomly
selected elements of the permutation) and cycle crossover for permutations. The
authors of CEGO used a budget of $10^4$ evaluations using the surrogate-model
for each run of the GA, however, with such setting, each run of CEGO requires
more than a week of computation time, which was infeasible for us, hence, we
set a value of \textcolor{red}{$10^3$}.

@@

The CPU time required for a single run of CEGO using these settings is larger
than a week.  For simplicity, we use Kendall Tau distance~\citep{?} in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance. We plan to extend our analysis of UMM to other
distance measures and to the dynamic selection of distance
measures~\citep{ZaeStoBar2014:ppsn}.

@@

Table~\ref{tab:results} shows overall results over all instances evaluated (excluding the synthetic LOP instances). In particular, the mean fitness (and standard deviation) of the best solution found at the end of each run,
\MANUEL{is the CI for CEGO $-$ UMM or UMM $-$ CEGO? I would prefer}
In terms of best fitness achieved on each run, and taking into account the
random behaviour observed in some instances and discussed above,

@@

\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl*{3}{r}}

@@

            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI for the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}

>>>>

Borda and uBorda are equivalent when $w(\sigma)$ is constant for every $\sigma$. However, in other case uBorda ranking will be closer to the rankings in $S$ with smaller value of $w(\sigma)$. Roughly speaking, it is equivalent to replicating in the sample the $\sigma$ with low values of $w(\sigma$).
%Intuitively, the uBorda ranking a given sample of permutations $S$\MANUEL{X What is $S$?} is equivalent to the Borda ranking of $S'$, being $S'$ an extension of $S$ where each each $\sigma\in S$ has been replicated proportionally to its weight $w(\sigma)$.\MANUEL{X so $w$ is a weight function from $w\colon S_n \to \mathbb{R}$?} %
Clearly, the choice of  $w(\sigma)$ depends on the relevant property of a ranking in a particular domain. For example, uBorda has been shown to have nice theoretical properties for the online estimation of the parameters of a sample with concept drift~\cite{}.\MANUEL{X where? Do we miss a citation here?\ekhine{}{to be processed, arxiv} Maybe you can create a bibentry with the details that you know already.}

@@

\subsubsection{CEGO.}
We use the implementation of GECO provided by the
authors.\footnote{\url{https://cran.r-project.org/package=CEGO}} %
Following the authors of
CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use a GA to optimize
the surrogate models, with population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements) and
cycle crossover for permutations. To generate each new solution, CEGO runs the
GA using the model as a surrogate of the true fitness function.  The authors of
CEGO used a budget of $10^4$ evaluations of the surrogate-model for each run of
the GA. However, with such a setting, one run of CEGO with a budget of $m=400$
evaluations of the true fitness function requires more than a week of
computation time, which was infeasible for our study. Hence, we set the budget of the GA to $10^3$. Although this means that the results of CEGO reported here could, in principle, improved with a higher GA budget  we believe

@@

The CPU time required for a single run of CEGO using these settings is larger
than a week.  For simplicity, we use Kendall's $\tau$ distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance. We plan to extend our analysis of UMM to other
distance measures and to the dynamic selection of distance
measures~\citep{ZaeStoBar2014:ppsn}.

@@

Table~\ref{tab:results} shows overall results over all instances evaluated (excluding the synthetic LOP instances). In particular, the mean fitness (and standard deviation) of the best solution found at the end of each run,
In terms of best fitness achieved on each run, and taking into account the
random behaviour observed in some instances and discussed above,

@@

\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}

@@

            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
